When, why, and how to avoid, prefer, or tolerate inbreeding

### 2018-03-01 presentation/inbreeding.Rmd
More progress

@@

@@

- Inbreeding depression ($\delta$) generally increases with inbreeding coefficient ($f$)

@@

>>>>

<style type="text/css">
body p {
  color: #000000;
}
</style>

@@

## Inbreeding and its consequences for evolution {.smaller}

![](images/opening.png)

<div align="left" style="line-height: 0.6em;">
<span style="font-size: 14px;">
1. [Wibowo Djatmiko](https://commons.wikimedia.org/wiki/User:Wie146). 2. [George Shuklin](https://commons.wikimedia.org/wiki/User:George_Shuklin). 3. [Natalie Pilakouta](https://www.nataliepilakouta.com/). 4. [Neale Monks](https://en.wikipedia.org/wiki/User:Neale_Monks). 5. [Jane Reid](https://www.abdn.ac.uk/ibes/profiles/jane.reid). 6. [André Karwath](https://commons.wikimedia.org/wiki/User:Aka). 7. [Benjamin Twist](https://commons.wikimedia.org/wiki/User:Benjamint444) 8. [Heinz Seehagel](https://de.wikipedia.org/wiki/Benutzer:HaSee). 
</span></div>

<!---
<hr>
<span style="font-size: 14px;">
1. *Poecilia reticula* image: [Wibowo_Djatmiko](https://commons.wikimedia.org/wiki/User:Wie146) <br>
</span>
--->

@@

- Inbreeding depression ($\delta$) increases with inbreeding coefficient ($f$)

@@

## General individual-based model assumptions

- Non-overlapping generations
